Subsegmental language detection in Celtic language text

### 2014-05-08 codeswitch-cltw-2014/codeswitch.tex
intro added v1
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52636 72bbbca6-d526-0410-a7d9-f06f51895060

\section{Introduction}
\label{intro}

\cite{lyu2006}

>>>>

\section{Introduction}
\label{intro}
With the increase in multilingualism and the adoption of ‘another’ acceptable language apart from the usual creates a change in the data. This change can be looked upon as bad when we are faced with the burden of upgrading systems to adapt to it, on the other hand such change is 
unavoidable and has to be welcomed. The good part is that the user or the speaker feels more comfortable in expressing their opinions. Such change directly requires us to upgrade our current systems \cite{fung2008multilingual} so that the processing or the analysis of the data is in no way compromised.\\
   Such code switching is more common in less formal ways of communication like on chats, forums and social media. Our motivation is to build a detection scheme which can sub-segment such sentences to the primary and secondary language tags and then prepare this to be processed further by modules which make use of this information to analyse useful information from this data. Specially in the case of languages like Irish, Breton and Welsh where the native speakers are very less, these people reach out to others and most of their posts are code-switched. Rather than promoting research based on monolingual technologies we would like to adopt to the trend and try to help other researchers in understanding this data in a better way.
\cite{lyu2006}
